Red, Blue, or Purple? 2024’s Battleground States Tell a Story

### 2024-11-04 paper/paper.qmd
discussion references added

This discussion examines the effectiveness and limitations of the election prediction model, with a focus on the factors that impact its accuracy and sensitivity to shifts in voter sentiment. The model integrates various adjustments, including state effect, pollster and pollscore effect, and days to election effect. The implications of these findings are considered, and potential areas for improvement in future forecasting efforts are highlighted.

@@

The model faces certain limitations related to both poll score reliability and recency adjustments, which may reduce its sensitivity to key factors affecting voter sentiment. Since poll score reliability shows a weak correlation with support percentages for certain candidates, this term might have small contributions to the overall prediction accuracy. This suggests that the model could potentially perform just as well with reduced weighting, or even without inclusion of this factor, simplifying the model structure without sacrificing accuracy. By reducing the emphasis on poll score reliability, the model could instead focus more on factors with a stronger influence on predictions, leading to a more streamlined and efficient approach.

@@

Moreover, future developments could improve the pollster and pollscore effects by incorporating machine learning techniques to dynamically assess pollster credibility based on historical performance. This could involve tracking each pollster’s accuracy across multiple election cycles and adjusting poll scores accordingly, instead of relying on fixed scores. By integrating a more adaptive assessment of pollster reliability, the model could mitigate the influence of outliers and increase its robustness in handling polling data from diverse sources. This changes would not only enhance accuracy but also reduce the risk of introducing systematic biases from overly influential or less reliable pollsters.

>>>>

This discussion examines the effectiveness and limitations of the election prediction model, with a focus on the factors that impact its accuracy and sensitivity to shifts in voter sentiment (@citeAccuracy). The model integrates various adjustments, including state effect, pollster and pollscore effect, and days to election effect. The implications of these findings are considered, and potential areas for improvement in future forecasting efforts are highlighted.

@@

The model faces certain limitations related to both poll score reliability and recency adjustments, which may reduce its sensitivity to key factors affecting voter sentiment (@citePollError). Since poll score reliability shows a weak correlation with support percentages for certain candidates, this term might have small contributions to the overall prediction accuracy. This suggests that the model could potentially perform just as well with reduced weighting, or even without inclusion of this factor, simplifying the model structure without sacrificing accuracy. By reducing the emphasis on poll score reliability, the model could instead focus more on factors with a stronger influence on predictions, leading to a more streamlined and efficient approach.

@@

Moreover, future developments could improve the pollster and pollscore effects by incorporating machine learning techniques to dynamically assess pollster credibility based on historical performance. This could involve tracking each pollster’s accuracy across multiple election cycles and adjusting poll scores accordingly, instead of relying on fixed scores (@cite2020Election). By integrating a more adaptive assessment of pollster reliability, the model could mitigate the influence of outliers and increase its robustness in handling polling data from diverse sources. This changes would not only enhance accuracy but also reduce the risk of introducing systematic biases from overly influential or less reliable pollsters.
